TKT RNAseq Experiment: Differential Expression Analysis

### 2023-06-21 TKT_RNAseq/R Code/EdgeR_Analysis.Rmd
Count and metadata using trimmed data
Fixed row names on TKT.EdgeR.Table.csv

groups2 = groups[setdiff(row.names(groups), c("GR.F3", "TktDfWT.F3")),]##"WT.F3",

@@

>>>>

groups2 = groups[setdiff(row.names(groups), c("GR.F3", "WT.F3", "TktDfWT.F3")),]

@@

TKT.EdgeR2 = data.frame(GRF.CxDf = GR.F.CxDf2[row.names(cpmdata2),'FDR'],
                        GRF.CxOE = GR.F.CxOE2[row.names(cpmdata2),'FDR'],

                        WTF.CxDf = WT.F.CxDf2[row.names(cpmdata2),'FDR'],
                        WTF.CxOE = WT.F.CxOE2[row.names(cpmdata2),'FDR'],

                        GRxWT.FC = GRxWT.F2[row.names(cpmdata2),'FDR'],
                        GRxWT.FDf = GRxWT.FDf2[row.names(cpmdata2),'FDR'],
                        GRxWT.FOE = GRxWT.FOE2[row.names(cpmdata2),'FDR'],

                        GRM.CxDf = GR.M.CxDf2[row.names(cpmdata2),'FDR'],
                        GRM.CxOE = GR.M.CxOE2[row.names(cpmdata2),'FDR'],

                        WTM.CxDf = WT.M.CxDf2[row.names(cpmdata2),'FDR'],
                        WTM.CxOE = WT.M.CxOE2[row.names(cpmdata2),'FDR'],

                        GRxWT.MC = GRxWT.M2[row.names(cpmdata2),'FDR'],
                        GRxWT.MDf = GRxWT.MDf2[row.names(cpmdata2),'FDR'],
                        GRxWT.MOE = GRxWT.MOE2[row.names(cpmdata2),'FDR'])

##write.csv(cpmdata2, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT_cpmdata.csv")
##write.csv(groups2, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.metadata.csv")
##write.csv(TKT.EdgeR2, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.EdgeR.Table.csv")
